Stay in shape! Homework exam II

### 2016-04-04 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
extended the bonus to be more 1 point worthy :p

\subsection{Bonus}
Applying what we've learned above we know we can handle ranges by using
binary trees. For single values we can use interval trees.
So suppose we know that $X$ will be an interval. Then the main tree will
be a binary tree sorting on $x$ where each node has a two sub-binary trees $y$
and $z$.
When we start reporting for x we'll choose the associated subtree which
is the interval query.
If $Y$ is an interval then we choose the $y$ subtree.
In the $y$ tree nodes have associated structures that are interval trees
on $z$.
If $Z$ is the interval then we choose the $z$ subtree. In $z$ subtree
there is again an associated structure for each node which is an interval
tree on $y$.
We can create another structure for when $X$ is not an interval. Similar
to the one above so that we can handle any range query.

The storage requirement is:

@@

Because the main tree is amplified additionally in size by an extra associated
structure depth.
The query time is:

Because there are 3 trees to traverse and we still need to report the answers.
\section{Voronoi nearest neighbour\emph{s}}
\subsection{Storage}
The original data structure was already of order:

>>>>

\newpage
\subsection{Bonus}
Let $S=\{s_1,\dots,s_n\}$ be a set of $n$ line segments in space each
of which is parallel to the x-axis, y-axis or z-axis.
\paragraph{Structure} We use a data-structure whose main tree is a balanced
binary search tree on the $x$ coordinates of the line segments of $S$.
For each interval node $v$, we have a canonical subset $S_v\subseteq S$
of all line segments that appear in the subtree rooted at $v$. The
set $S_v$ is stored in two associated structures with $v$ as well:
these are again balanced binary trees, one is on the $y$ coordinates
of the line segments of $S_v$ and the other one is the $z$ coordinates
of the line segments of $S_v$. These associated structures are similar
in structure to the main tree however the associated structures of their
nodes are interval trees the $y$
subtree has associated interval trees based on the $z$ interval and
the $z$ tree has it based on the $y$ interval.
This structure cannot treat $x$ intervals however. To also treat
$x$ intervals we create another tree similar to the one above, however
we substitute $x$ by $y$ and $y$ by $x$.
\paragraph{Query algorithm} If $X$ is an interval we use the first tree.
So we go down the tree until we encounter a split node. If we do we
split up the algorithm, one side starts reporting left and the other one
right. However we need to choose the right associated
structure. We first want to do the range query and save the single value for
last. So if $Y$ in this case is a range query we choose the $y$ associated
structure when reporting.
The report call will query the associated structures similarly
to the select of `2.c'. Only in this case the dimension name of $x$ will be
replaced by $z$.
\paragraph{Query time}
The query time is:

Because there are 3 trees to traverse and we still need to report the answers.
\paragraph{Storage}
The storage requirement is:

@@

Because the main tree is amplified additionally in size by an extra associated
structure depth.
\section{Voronoi nearest neighbour\emph{s}}
\subsection{Storage}
The original data structure was already of order:
